### 2020-06-19 system-model.tex
:pencil: Splitting ratio optimization

\begin{section}{Single-User Optimization}
	Consider a single-user waveform and IRS optimization problem where $\boldsymbol{\alpha}=\boldsymbol{1}^{N \times 1}$. We characterize the rate-energy region through a current maximization problem subject to transmit power, rate, and IRS constraints
	\begin{maxi!}
			{\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho}{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)}{\label{op:su}}{}
			\addConstraint{\frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P})\le{P}}
			\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert(h_{D,n}+\boldsymbol{v}_n^H\boldsymbol{\phi})w_{I,n}\rvert^2}{\sigma_n^2}\right)} \ge \bar{R}}
			\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}
		\end{maxi!}
	Problem \ref{op:su} is intricate due to the non-convex objective function with coupled variables. In the next section, we propose waveform and phase shift design algorithms for frequency-flat and frequency-selective IRS, respectively.

@@

				& \ge 2 (t_{I,0}^{(i)})(t_{I,0}^{(i-1)}) - (t_{I,0}^{(i-1)})^2\label{eq:t_approx_begin}\\

@@

				& \quad - \frac{1}{4}(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)})^2 - \frac{1}{4}(t_{I,0}^{(i)} - t_{P,0}^{(i)})^2\label{eq:t_approx_end}

@@

			\ref{eq:t_approx_begin} -- \ref{eq:t_approx_end} provide lower bounds to corresponding terms such that the approximated current function at iteration $i$ is given in \ref{eq:z_irs_approx}.

@@

		\begin{subsubsection}{Transmit Waveform Optimization}
			Consider the waveform optimization subproblem. Once $\boldsymbol{\Phi}$ and $\rho$ are obtained, introduce auxiliary variables
			\begin{equation}\label{eq:t'}
				t_{I/P,n}' = \boldsymbol{w}_{I/P}^H \boldsymbol{H}_n^* \boldsymbol{w}_{I/P} = \mathrm{Tr}(\boldsymbol{H}_n^*\boldsymbol{W}_{I/P})
			\end{equation}
			Therefore, \ref{eq:z_k_waveform} rewrites as
			\begin{equation}\label{eq:z_waveform}
				\begin{split}
					z(\boldsymbol{W}_I,\boldsymbol{W}_P)
					&=\frac{1}{2} \beta_2 \rho (t'_{I,0}+t'_{P,0})\\
					&\quad+\frac{3}{8} \beta_4 \rho^2 \left(2(t'_{I,0})^2 + \sum_{n=-N+1}^{N-1}{t'_{P,n}(t'_{P,n})^*}\right)\\
					&\quad+\frac{3}{2} \beta_4 \rho^2 t'_{I,0}t'_{P,0}
				\end{split}
			\end{equation}
			Since \ref{eq:z_waveform} and \ref{eq:z_irs} are in the same form, we reuse \ref{eq:t_approx_begin} -- \ref{eq:t_approx_end} and bound \ref{eq:z_waveform} by replacing $t_{I/P,n}$ with $t_{I/P,n}'$ in \ref{eq:z_irs_approx}.	Hence, problem \ref{op:su} is transformed to
			\begin{maxi!}
				{\boldsymbol{W}_I,\boldsymbol{W}_P}{\tilde{z}(\boldsymbol{W}_I,\boldsymbol{W}_P)}{\label{op:su_waveform}}{\label{eq:su_waveform_target}}
				\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)W_{I,n,n}\lvert h_n \rvert^2}{\sigma_n^2}\right)} \ge \bar{R}\label{eq:su_waveform_constraint}}
				\addConstraint{\frac{1}{2}\left(\mathrm{Tr}(\boldsymbol{W}_I)+\mathrm{Tr}(\boldsymbol{W}_P)\right) \le P}
				\addConstraint{\boldsymbol{W}_{I/P} \succeq 0}
				\addConstraint{\mathrm{rank}(\boldsymbol{W}_{I/P})=1\label{co:waveform_rank}}
			\end{maxi!}
			We then perform SDR and solve the optimal waveform matrix $\boldsymbol{W}_{I/P}^{\star}$ iteratively by interior-point method. $\boldsymbol{w}_I^{\star}$ and $\boldsymbol{w}_P^{\star}$ can also be extracted using randomized vectors $\boldsymbol{r}_q \in \mathbb{C}^{(L+1) \times 1}, \ q=1,\dots,Q$, whose entries are uniformly distributed on the unit circle $r_{q,n}=e^{j\xi}$, $\xi \sim \mathcal{U}[0,2\pi)$. The algorithm is summarized in Algorithm \ref{al:ff_waveform}.
			\begin{algorithm}
				\caption{FF-IRS: Transmit Waveform Optimization}
				\label{al:ff_waveform}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\bar{R},P,Q,\sigma_n,\boldsymbol{H}_n,\boldsymbol{R}_n \ \forall n$ by \ref{eq:R_n,phi}
					\State \textbf{Initialize} $i \leftarrow 0$, $\boldsymbol{W}_{I/P}^{(0)}$, $t_{I/P,n}^{\prime (0)} \ \forall n$
					\Repeat
					\State $i \leftarrow i + 1$
					\State Obtain waveform matrices $\boldsymbol{W}_{I/P}^{(i)}$ by solving problem \ref{op:su_waveform}
					\State Update auxiliary $t_{I/P,n}^{\prime (i)} \forall n$ by \ref{eq:t'} for SCA
					\Until $\lvert (z^{(i)}-z^{(i-1)}) / z^{(i)} \rvert \le \epsilon$
					\State Perform EVD $\boldsymbol{W}_{I/P}^{\star}=\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}^H$
					\State Generate random vectors $\boldsymbol{r}_q \ \forall q$ with entries uniformly distributed on the unit circle
					\State Construct candidate waveform vectors $\boldsymbol{w}_{I/P,r}=\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{W}_{I/P}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q$ and matrices $\boldsymbol{W}_{I/P,q}=\boldsymbol{w}_{I/P,q}\boldsymbol{w}_{I/P,q}^H  \ \forall q$
					\State Select best solution $\boldsymbol{W}_{I/P}^\star$ and $\boldsymbol{w}_{I/P}^\star$ for problem \ref{op:su_waveform}
					\State \textbf{Output} $\boldsymbol{w}_{I/P}^\star$
				\end{algorithmic}
			\end{algorithm}
		\end{subsubsection}

		\begin{subsection}{WIT initialization}
			To characterize the R-E region, we initialize the algorithm to WIT mode and reduce the rate constraint gradually to obtain the boundary points. Consider a rate maximization problem with given information waveform $\boldsymbol{w}_I$ and power splitting ratio $\rho = 0$ as
			\begin{maxi!}
				{\boldsymbol{\Phi}}{\sum_{n}{\log_2\left(1+\frac{\lvert{w}_{I,n}\rvert^2\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)}}{\label{op:su_irs_wit}}{}
				\addConstraint{\boldsymbol{\Phi}_{l,l}=1, \quad l=1,\dots,L+1}
				\addConstraint{\boldsymbol{\Phi}\succeq{0}}
				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1}
			\end{maxi!}
			Problem \ref{op:su_irs_wit} can be solved after SDR. Similar to section \ref{se:fs_irs}, a best solution $\bar{\boldsymbol{\phi}}^\star$ can be obtained via Gaussian randomization method and $\boldsymbol{\phi}^\star$ can be recovered by $\phi_l^\star=\phi_l^\star/\phi_{L+1}^\star, \ l=1,\dots,L$. After constructing composite channel $\boldsymbol{h}$ by \ref{eq:h_k}, we use water-filling algorithm and matched filter to obtain optimal power allocation $p_n^\star=\lvert w_{I,n} \rvert^2$ and beamforming phase $\psi_{I,n}^\star=-\bar{\psi}_n$, respectively. Therefore, the optimal information waveform at subband $n$ is
			\begin{equation}\label{eq:w_wit}
				w_{I,n}^\star=\sqrt{p_n^\star}e^{j \psi_{I,n}^\star}
			\end{equation}
			We update IRS phase shift by \ref{op:su_irs_wit} and information waveform by \ref{eq:w_wit} until convergence. The WIT initialization algorithm is summarized in \ref{al:ff_wit}.
			\begin{algorithm}
				\caption{FF-IRS: WIT Initialization}
				\label{al:ff_wit}
				\begin{algorithmic}[1]
					\State \textbf{Input} $P, Q, \boldsymbol{R}_n, \sigma_n \ \forall n$
					\State \textbf{Initialize} $i \leftarrow 0$, $\boldsymbol{w}_I^{(0)}$
					\Repeat
					\State $i \leftarrow i + 1$
					\State Obtain IRS matrix $\boldsymbol{\Phi}^{(i)}$ by solving problem \ref{op:su_irs_wit}
					\State Perform EVD $\boldsymbol{\Phi}^{(i)}=\boldsymbol{U}_{\boldsymbol{\Phi}^{(i)}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{(i)}}\boldsymbol{U}_{\boldsymbol{\Phi}^{(i)}}^H$
					\State Generate random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}) \ \forall q$
					\State Construct candidate IRS vectors $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}_{\boldsymbol{\Phi}^{(i)}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{(i)}}^{\frac{1}{2}}\boldsymbol{r}_q\right)}$ and matrices $\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H  \ \forall q$
					\State Select best solution $(\boldsymbol{\Phi}^{(i)})^\star$ and $(\boldsymbol{\phi}^{(i)})^\star$ for problem \ref{op:su_irs_wit}
					\State Update composite channel $(\boldsymbol{h}^{(i)})^\star$ by \ref{eq:h_k}
					\State Obtain optimal power allocation $p_n^{(i)} \ \forall n$ by water-filling algorithm
					\State Obtain optimal waveform phase $(\psi_{I,n}^{(i)})^\star \ \forall n$ by \ref{eq:psi}
					\State Update information waveform $(\boldsymbol{w}_I^{(i)})^\star$ by \ref{eq:w_wit}
					\Until $\lvert (R^{(i)}-R^{(i-1)}) / R^{(i)} \rvert \le \epsilon$
					\State \textbf{Output} $\boldsymbol{w}_I^\star, \boldsymbol{\phi}^\star$
				\end{algorithmic}
			\end{algorithm}
		\end{subsection}
	\end{subsection}
\end{section}

>>>>

\begin{section}{Single-User Optimization}
	Consider a single-user waveform and IRS optimization problem where $\boldsymbol{\alpha}=\boldsymbol{1}^{N \times 1}$. We characterize the rate-energy region through a current maximization problem subject to transmit power, rate, and IRS constraints
	\begin{maxi!}
			{\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho}{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)}{\label{op:su}}{}
			\addConstraint{\frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P})\le{P}}
			\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert(h_{D,n}+\boldsymbol{v}_n^H\boldsymbol{\phi})w_{I,n}\rvert^2}{\sigma_n^2}\right)} \ge \bar{R}}
			\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}
			\addConstraint{0 \le \rho \le 1}
		\end{maxi!}
	Problem \ref{op:su} is intricate due to the non-convex objective function with coupled variables. In the next section, we propose waveform and phase shift design algorithms for frequency-flat and frequency-selective IRS, respectively.

@@

				& \ge 2 t_{I,0}^{(i)}t_{I,0}^{(i-1)} - (t_{I,0}^{(i-1)})^2\label{eq:t_{I,0}_square}\\

@@

				& \quad - \frac{1}{4}(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)})^2 - \frac{1}{4}(t_{I,0}^{(i)} - t_{P,0}^{(i)})^2\label{eq:t_{I/P,0}}

@@

			\ref{eq:t_{I,0}_square} -- \ref{eq:t_{I/P,0}} provide lower bounds to corresponding terms such that the approximated current function at iteration $i$ is given in \ref{eq:z_irs_approx}.

@@

		\begin{subsubsection}{Transmit Waveform Optimization}
			Consider the waveform optimization subproblem. Once $\boldsymbol{\Phi}$ and $\rho$ are obtained, introduce auxiliary variables
			\begin{equation}\label{eq:t'}
				t_{I/P,n}' = \boldsymbol{w}_{I/P}^H \boldsymbol{H}_n^* \boldsymbol{w}_{I/P} = \mathrm{Tr}(\boldsymbol{H}_n^*\boldsymbol{W}_{I/P})
			\end{equation}
			Therefore, \ref{eq:z_k_waveform} rewrites as
			\begin{equation}\label{eq:z_waveform}
				\begin{split}
					z(\boldsymbol{W}_I,\boldsymbol{W}_P)
					&=\frac{1}{2} \beta_2 \rho (t'_{I,0}+t'_{P,0})\\
					&\quad+\frac{3}{8} \beta_4 \rho^2 \left(2(t'_{I,0})^2 + \sum_{n=-N+1}^{N-1}{t'_{P,n}(t'_{P,n})^*}\right)\\
					&\quad+\frac{3}{2} \beta_4 \rho^2 t'_{I,0}t'_{P,0}
				\end{split}
			\end{equation}
			Since \ref{eq:z_waveform} and \ref{eq:z_irs} are in the same form, we reuse \ref{eq:t_{I,0}_square} -- \ref{eq:t_{I/P,0}} and bound \ref{eq:z_waveform} by replacing $t_{I/P,n}$ with $t_{I/P,n}'$ in \ref{eq:z_irs_approx}. Hence, problem \ref{op:su} is transformed to
			\begin{maxi!}
				{\boldsymbol{W}_I,\boldsymbol{W}_P}{\tilde{z}(\boldsymbol{W}_I,\boldsymbol{W}_P)}{\label{op:su_waveform}}{\label{eq:su_waveform_target}}
				\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)W_{I,n,n}\lvert h_n \rvert^2}{\sigma_n^2}\right)} \ge \bar{R}\label{eq:su_waveform_constraint}}
				\addConstraint{\frac{1}{2}\left(\mathrm{Tr}(\boldsymbol{W}_I)+\mathrm{Tr}(\boldsymbol{W}_P)\right) \le P}
				\addConstraint{\boldsymbol{W}_{I/P} \succeq 0}
				\addConstraint{\mathrm{rank}(\boldsymbol{W}_{I/P})=1\label{co:waveform_rank}}
			\end{maxi!}
			We then perform SDR and solve the optimal waveform matrix $\boldsymbol{W}_{I/P}^{\star}$ iteratively by interior-point method. $\boldsymbol{w}_I^{\star}$ and $\boldsymbol{w}_P^{\star}$ can also be extracted using randomized vectors $\boldsymbol{r}_q \in \mathbb{C}^{(L+1) \times 1}, \ q=1,\dots,Q$, whose entries are uniformly distributed on the unit circle $r_{q,n}=e^{j\xi}$, $\xi \sim \mathcal{U}[0,2\pi)$. The algorithm is summarized in Algorithm \ref{al:ff_waveform}.
			\begin{algorithm}
				\caption{FF-IRS: Transmit Waveform Optimization}
				\label{al:ff_waveform}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\bar{R},P,Q,\sigma_n,\boldsymbol{H}_n,\boldsymbol{R}_n \ \forall n$ by \ref{eq:R_n,phi}
					\State \textbf{Initialize} $i \leftarrow 0$, $\boldsymbol{W}_{I/P}^{(0)}$, $t_{I/P,n}^{\prime (0)} \ \forall n$
					\Repeat
					\State $i \leftarrow i + 1$
					\State Obtain waveform matrices $\boldsymbol{W}_{I/P}^{(i)}$ by solving problem \ref{op:su_waveform}
					\State Update auxiliary $t_{I/P,n}^{\prime (i)} \forall n$ by \ref{eq:t'} for SCA
					\Until $\lvert (z^{(i)}-z^{(i-1)}) / z^{(i)} \rvert \le \epsilon$
					\State Perform EVD $\boldsymbol{W}_{I/P}^{\star}=\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}^H$
					\State Generate random vectors $\boldsymbol{r}_q \ \forall q$ with entries uniformly distributed on the unit circle
					\State Construct candidate waveform vectors $\boldsymbol{w}_{I/P,r}=\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{W}_{I/P}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q$ and matrices $\boldsymbol{W}_{I/P,q}=\boldsymbol{w}_{I/P,q}\boldsymbol{w}_{I/P,q}^H  \ \forall q$
					\State Select best solution $\boldsymbol{W}_{I/P}^\star$ and $\boldsymbol{w}_{I/P}^\star$ for problem \ref{op:su_waveform}
					\State \textbf{Output} $\boldsymbol{w}_{I/P}^\star$
				\end{algorithmic}
			\end{algorithm}
		\end{subsubsection}

		\begin{subsubsection}{Receive Splitting Ratio Optimization}
			We then optimize the power splitting ratio $\rho$ for any fixed phase shift $\boldsymbol{\phi}$ and waveform $\boldsymbol{w}_{I/P}$. In this case, the output DC current is also expressed by \ref{eq:z_waveform} but as a function of $\rho$ with constant $t_{I/P,n}'$ defined in \ref{eq:t'}. Therefore, problem \ref{op:su} is transformed to
			\begin{maxi!}
				{\rho}{z(\rho)}{\label{op:su_ratio}}{\label{eq:su_ratio_target}}
				\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert h_n w_n \rvert^2}{\sigma_n^2}\right)} \ge \bar{R}\label{eq:su_ratio_constraint}}
				\addConstraint{0 \le \rho \le 1}
			\end{maxi!}
			It can be observed that $z(\rho)$ is a monotonically increasing function of $\rho$ such that the maximum value of \ref{eq:su_ratio_target} is achieved when equality in \ref{eq:su_ratio_constraint} holds, namely
			\begin{equation}\label{eq:rho}
				\prod_n \left(1 + \frac{(1 - \rho^\star)\lvert h_n w_n \rvert^2}{\sigma_n^2}\right) = 2^{\bar{R}}
			\end{equation}
			The optimal power splitting ratio can be obtained from \ref{eq:rho} in closed form.
		\end{subsubsection}

		\begin{subsubsection}{WIT Initialization}
			To characterize the R-E region, we initialize the algorithm to WIT mode and reduce the rate constraint gradually to obtain the boundary points. Consider a rate maximization problem with given information waveform $\boldsymbol{w}_I$ and power splitting ratio $\rho = 0$ as
			\begin{maxi!}
				{\boldsymbol{\Phi}}{\sum_{n}{\log_2\left(1+\frac{\lvert{w}_{I,n}\rvert^2\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)}}{\label{op:su_irs_wit}}{}
				\addConstraint{\boldsymbol{\Phi}_{l,l}=1, \quad l=1,\dots,L+1}
				\addConstraint{\boldsymbol{\Phi}\succeq{0}}
				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1}
			\end{maxi!}
			Problem \ref{op:su_irs_wit} can be solved after SDR. Similar to section \ref{se:fs_irs}, a best solution $\bar{\boldsymbol{\phi}}^\star$ can be obtained via Gaussian randomization method and $\boldsymbol{\phi}^\star$ can be recovered by $\phi_l^\star=\phi_l^\star/\phi_{L+1}^\star, \ l=1,\dots,L$. After constructing composite channel $\boldsymbol{h}$ by \ref{eq:h_k}, we use water-filling algorithm and matched filter to obtain optimal power allocation $p_n^\star=\lvert w_{I,n} \rvert^2$ and beamforming phase $\psi_{I,n}^\star=-\bar{\psi}_n$, respectively. Therefore, the optimal information waveform at subband $n$ is
			\begin{equation}\label{eq:w_wit}
				w_{I,n}^\star=\sqrt{p_n^\star}e^{j \psi_{I,n}^\star}
			\end{equation}
			We update IRS phase shift by \ref{op:su_irs_wit} and information waveform by \ref{eq:w_wit} until convergence. The WIT initialization algorithm is summarized in \ref{al:ff_wit}.
			\begin{algorithm}
				\caption{FF-IRS: WIT Initialization}
				\label{al:ff_wit}
				\begin{algorithmic}[1]
					\State \textbf{Input} $P, Q, \boldsymbol{R}_n, \sigma_n \ \forall n$
					\State \textbf{Initialize} $i \leftarrow 0$, $\boldsymbol{w}_I^{(0)}$
					\Repeat
					\State $i \leftarrow i + 1$
					\State Obtain IRS matrix $\boldsymbol{\Phi}^{(i)}$ by solving problem \ref{op:su_irs_wit}
					\State Perform EVD $\boldsymbol{\Phi}^{(i)}=\boldsymbol{U}_{\boldsymbol{\Phi}^{(i)}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{(i)}}\boldsymbol{U}_{\boldsymbol{\Phi}^{(i)}}^H$
					\State Generate random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}) \ \forall q$
					\State Construct candidate IRS vectors $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}_{\boldsymbol{\Phi}^{(i)}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{(i)}}^{\frac{1}{2}}\boldsymbol{r}_q\right)}$ and matrices $\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H  \ \forall q$
					\State Select best solution $(\boldsymbol{\Phi}^{(i)})^\star$ and $(\boldsymbol{\phi}^{(i)})^\star$ for problem \ref{op:su_irs_wit}
					\State Update composite channel $(\boldsymbol{h}^{(i)})^\star$ by \ref{eq:h_k}
					\State Obtain optimal power allocation $p_n^{(i)} \ \forall n$ by water-filling algorithm
					\State Obtain optimal waveform phase $(\psi_{I,n}^{(i)})^\star \ \forall n$ by \ref{eq:psi}
					\State Update information waveform $(\boldsymbol{w}_I^{(i)})^\star$ by \ref{eq:w_wit}
					\Until $\lvert (R^{(i)}-R^{(i-1)}) / R^{(i)} \rvert \le \epsilon$
					\State \textbf{Output} $\boldsymbol{w}_I^\star, \boldsymbol{\phi}^\star$
				\end{algorithmic}
			\end{algorithm}
		\end{subsubsection}
	\end{subsection}
\end{section}
